{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis, Truth or Just a Dream?}

### 2025-07-19 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w< finally working

                F(z) + \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2} \Vert z - x\Vert^2

@@

        Otherwise we can assume $\prob(\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0) > 0$ and, the expectation has: 

@@

                & \expect_kF(x_k) - F(\bar x) - \frac{\alpha_k^2(L - \epsilon_k)}{2}\expect_k \left[\Vert v_k - \bar x\Vert^2\right]

@@

                    + \frac{\alpha_{k - 1}L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2

@@

            \textcolor{red}{Explanations for \circled{1}, \circled{2}, \circled{3} are not done yet}. 
            The above produces the following inequality: 

@@

                    + \frac{\alpha_{k - 1}L\rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2

@@

@@

                \frac{1 - \alpha_k}{2(L - \sigma)}\left(

>>>>

                F(z) - \expect F(\tilde x) + \frac{\max(B, L) - \mu}{2} \Vert z - x\Vert^2

@@

        Otherwise, we can assume $\prob(\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert > 0) > 0$ and, the expectation has: 

@@

@@

            In the edge case of $k = 0$, it has: 
                \expect_0 F(x_0) - F(\bar x)  
                + \frac{L - \epsilon}{2}\expect_0\left[\Vert \bar x - x_0\Vert^2\right]
                \frac{L - \mu}{2} \Vert \bar x - v_{-1}\Vert^2
                + \frac{\epsilon}{2}\expect_0\left[\Vert v_{-1} - x_0\Vert^2\right]. 

@@

            At \circled{1}, we used Lemma \ref{thm:jesen}. 
            For \circled{3}, we used Lemma \ref{lemma:seq-properties} (i) and (b) because the sequence $\alpha_k \le 1$, therefore $1 - \alpha_k \le 1$. 
            Next, $\alpha_0 = 1 > \mu/L$, Lemma \ref{lemma:seq-properties} (ii) applies too, hence it also has $L\alpha_k - \mu \ge 0$. 
            Since $L > \mu$ always, the coefficient on $\Vert x_{k - 1} - v_{k - 1}\Vert^2$ is always $\le 0$, therefore the term can be removed to give an inequality. 
            At \circled{3}, we used Lemma \ref{lemma:snag-identities} (ii). 
            Therefore, at the end the chain of inequalities from above produced the following inequality: 

@@

@@

            Next, we handle the Edge case of $k = 0$. 
            The base case has $\alpha_0 = 1$, and $v_{-1} = x_{-1}$. 
            Then, the following consequences will be immediate. 
            Fom Definition \ref{def:SNAG}, $\alpha_0 = 1$ makes $\tau_0 = 0$, so $y_0 = v_{-1}$. 
            Followed by it, $x_0 = \tilde {\mathbf T}_L(y_0 | F) = \widetilde{\mathbf T}_L(v_{-1} | F)$. 
            Therefore, we can apply Lemma \ref{lemma:pg-stoch-ineq} with $z = \bar x$, $\tilde x = x_0$, $x = v_{-1}$, and $\epsilon = \epsilon_0$ it yields: 
                F(z) - \expect_0 F(\tilde x)
                + \frac{L - \mu}{2} \Vert z - x\Vert^2
                - \frac{L - \epsilon}{2}\expect_0\left[\Vert z - \tilde x\Vert^2\right]
                + \frac{\epsilon}{2} \expect_0\left[\Vert x - \tilde x\Vert^2\right]
                F(\bar x) - \expect_0 F(x_0)
                + \frac{L - \mu}{2} \Vert \bar x - v_{-1}\Vert^2
                - \frac{L - \epsilon}{2}\expect_0\left[\Vert \bar x - x_0\Vert^2\right]
                + \frac{\epsilon}{2}\expect_0\left[\Vert v_{-1} - x_0\Vert^2\right].

@@

                \frac{1 - \alpha_k}{2(L - \mu)}\left(
